---
title: 'Dissertation Analysis: Time Remaining - Strategy'
author: "Jamiahus Walton"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: true
editor_options:
  chunk_output_type: inline
csl: apa.csl
bibliography: bibliography.bib
params:
  dependent_response_name_WithSpace: "Time Remaining"
  dependent_response_name_NoSpace: "TimeRemaining"
  dependent_response_team: "timeRemaining_team"
  dependent_response_ind: "timeRemaining_ind"
  dependent_response_DominateStrategy: "Dominate.Strategy"
  Strategy_GT_name_NoSpace: "Go.Together"
  Strategy_GT_name_WithSpace: "Go Together"
  Strategy_GA_name_NoSpace: "Go.Alone"
  Strategy_GA_name_WithSpace: "Go Alone"
---

```{r setup, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Tips for formatting in RMarkdown
# Link: https://monashbioinformaticsplatform.github.io/2017-11-16-open-science-training/topics/rmarkdown.html

# Equations
# Link: https://www.calvin.edu/~rpruim/courses/s341/S17/from-class/MathinRmd.html

# Create awesome HTML table with knitr::kableand kableExtra
# LinkL https://haozhu233.github.io/kableExtra/awesome_table_in_html.html

# Examples of how to use the ggrepel package
# Link: https://cran.r-project.org/web/packages/ggrepel/vignettes/ggrepel.html#examples

# Packages for data analysis
library(tidyverse)
library(lme4)
library(lmerTest)
library(emmeans)
library(svMisc)
library(MuMIn)
library(modelr)
library(sjstats)
library(robustlmm)
library(ggrepel)
library(knitr)
library(kableExtra)

# Functions used in documents ----
remove_measures_with_given_value <- function(data_set, col_name, value){
  rows_to_move <- which(as.vector(data_set[,col_name]) == value) 
  
  return(data_set[-rows_to_move,])
}

# Factor columns that need it.
re_factor_columns <- function(userData, columnNames){
  factorData <- userData
  for(column in columnNames){
    print(column)
    factorData[,column] <- factor(factorData[,column])
  }
  return(factorData)
}

# Model the data for the team level analysis ----
model_data_Target_Session <- function(df, dependent, model.type, is.team, is.robust){
  
  if(is.team){
    if(model.type == "null" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ 1 + (1|Team)")))
    } else if(model.type == "All"){
      lmer(data = df, as.formula(paste(dependent,"~ Target * SessionOrder + (1|Team)")))
    } else if(model.type == "NoInteraction" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ Target + SessionOrder + (1|Team)")))
    } else if(model.type == "NoInteraction_NoTarget" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ SessionOrder + (1|Team)")))
    } else if(model.type == "NoInteraction_NoSession" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ Target + (1|Team)")))
    } else if(model.type == "null" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ 1 + (1|Team)")))
    } else if(model.type == "All" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ Target * SessionOrder + (1|Team)")))
    } else if(model.type == "NoInteraction" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ Target + SessionOrder + (1|Team)")))
    } else if(model.type == "NoInteraction_NoTarget" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ SessionOrder + (1|Team)")))
    } else if(model.type == "NoInteraction_NoSession" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ Target + (1|Team)")))
    } else{
      stop("Model.type not supported")
    }
  } else {
    # Run this code if individual level model
    if(model.type == "null" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ 1 + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "All" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ Target * SessionOrder + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "NoInteraction" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ Target + SessionOrder + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "NoInteraction_NoTarget" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ SessionOrder + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "NoInteraction_NoSession"){
      lmer(data = df, as.formula(paste(dependent,"~ Target + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "null" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ 1 + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "All" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ Target * SessionOrder + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "NoInteraction" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ Target + SessionOrder + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "NoInteraction_NoTarget" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ SessionOrder + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "NoInteraction_NoSession" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ Target + (1|Team) + (1| Player_ID)")))
    } else{
      stop("Model.type not supported")
    }
  }
}

#Folder locations ----
figure_directory <- "C:\\Users\\jamia\\Box\\TMET2\\DATA TMET2\\Data_And_Calcuations\\Figures"
main_work_directory_name <- "C:\\Users\\jamia\\Box\\TMET2\\DATA TMET2\\Data_And_Calcuations\\Raw Data\\"

database_folder_name <- "Database"
file_name_output <- "team_player_aggragate_stats.csv"
folder_location_database <- paste(main_work_directory_name, database_folder_name, sep = "")
aggregate_folder_location <- paste(folder_location_database,"\\", file_name_output, sep = "") #This will combine the final file name and the desiered folder location

# Read aggregaate data ----
my_aggregate_data <- read.csv(file =  aggregate_folder_location)

clean_aggregate_data_stats <- remove_measures_with_given_value(data_set =  my_aggregate_data, col_name = "Condition", value = "A") # without none condition

# Re factor the columns
columns_to_refactor <- c("SessionOrder", 
                         "Team", 
                         "Player_ID", 
                         "Condition", 
                         "Dominate.Strategy", 
                         "Condition", 
                         "Target",
                         "Confident_team_comm_important_details_quickly")
clean_aggregate_data_stats <- re_factor_columns(clean_aggregate_data_stats, columns_to_refactor)

# What is the N for Teams ----
N_teams <- length(levels(factor(clean_aggregate_data_stats$Team)))

# What is the N for Inds ----
N_ind <- length(levels(factor(clean_aggregate_data_stats$Player_ID) ))

# Team data set ----
team_data <- clean_aggregate_data_stats %>%
  filter(Player == 1)

# Individual data set ----
ind_data <- clean_aggregate_data_stats

```

# Q: Is there exciting variation among the _`r params$dependent_response_name_WithSpace`_ metric that will help me understand the influence of the feedback condition?

## Team

```{r cache=FALSE}
y_label_team <- "Count"
x_label_team <- params$dependent_response_name_WithSpace
title_response_team <- paste("Distribution of", params$dependent_response_name_WithSpace, "(Team)")
plot_name <- paste("Histogram_", params$dependent_response_name_NoSpace, "_Team.png", sep = "")
setwd(figure_directory)

plot_data_team <- team_data %>%
  select(params$dependent_response_team, 
         params$dependent_response_DominateStrategy, 
         Target)

ggplot(data = plot_data_team) + 
  geom_histogram(aes_string(x = params$dependent_response_team), bins = 30) +
  facet_grid( . ~ .data[[params$dependent_response_DominateStrategy]]) +
  labs(title = title_response_team, x = x_label_team, y = y_label_team) +
  ggsave(filename = plot_name)
```

The distribution of both groups have a skew to the left.

```{r cache=FALSE}
y_label_team <- "Count"
x_label_team <- "Target"
title_response_team <- paste("Distribution of", params$dependent_response_name_WithSpace, "(Team)")
plot_name <- paste("Histogram_", params$dependent_response_name_NoSpace, "_ByTarget_Team.png", sep = "")
setwd(figure_directory)

plot_data_team <- team_data %>%
  select(params$dependent_response_team, 
         params$dependent_response_DominateStrategy, 
         Target)

ggplot(data = plot_data_team) + 
  geom_histogram(aes_string(x = params$dependent_response_team), bins = 25) +
  facet_grid(.data[[params$dependent_response_DominateStrategy]] ~ Target) +
  labs(title = title_response_team, x = x_label_team, y = y_label_team) +
  ggsave(filename = plot_name)

# Information about the N values in each condition
tableData <- team_data %>%
  group_by(Target, .data[[params$dependent_response_DominateStrategy]]) %>%
  summarise(N = length(.data[[params$dependent_response_team]]))

tableData %>%
  kable() %>%
  kable_styling()
```

I see no obvious pattern.

```{r}
y_label_team <- "Count"
x_label_team <- params$dependent_response_name_WithSpace
setwd(figure_directory)

plot_data_team <- team_data %>%
  select(params$dependent_response_team, 
         params$dependent_response_DominateStrategy,
         Target, 
         SessionOrder)

# Generate data by strategy
GA_plot_data_team <- plot_data_team %>%
  filter(.data[[params$dependent_response_DominateStrategy]] == params$Strategy_GA_name_WithSpace)

GT_plot_data_team <- plot_data_team %>%
  filter(.data[[params$dependent_response_DominateStrategy]] == params$Strategy_GT_name_WithSpace)

# Plot
 # GA
ggplot(data = GA_plot_data_team) + 
  geom_histogram(aes_string(x = params$dependent_response_team), bins = 30) +
  labs(title = paste("Distribution of", params$dependent_response_name_WithSpace, "(Team)","(", params$Strategy_GA_name_WithSpace ,")" ), x = x_label_team, y = y_label_team) +
  facet_grid( SessionOrder ~ Target) + 
  ggsave(filename = paste("Histogram_", params$dependent_response_name_NoSpace, "_ByTarget_BySessionOrder_", params$Strategy_GA_name_NoSpace, "_Team.png", sep = ""))

    # Information about the N values in each condition
GA_tableData <- GA_plot_data_team %>%
  select(params$dependent_response_team, Target, SessionOrder) %>%
  group_by(Target, SessionOrder) %>%
  summarise(N = length(.data[[params$dependent_response_team]]))

GA_tableData %>%
  kable(caption = paste("Data for ", params$Strategy_GA_name_WithSpace)) %>%
  kable_styling()

 # GT
ggplot(data = GT_plot_data_team) + 
  geom_histogram(aes_string(x = params$dependent_response_team), bins = 30) +
  labs(title = paste("Distribution of", params$dependent_response_name_WithSpace, "(Team)","(", params$Strategy_GT_name_WithSpace ,")" ), x = x_label_team, y = y_label_team) +
  facet_grid( SessionOrder ~ Target) + 
  ggsave(filename = paste("Histogram_", params$dependent_response_name_NoSpace, "_ByTarget_BySessionOrder_", params$Strategy_GT_name_NoSpace, "_Team.png", sep = ""))

    # Information about the N values in each condition
GT_tableData <- GT_plot_data_team %>%
  select(params$dependent_response_team, Target, SessionOrder) %>%
  group_by(Target, SessionOrder) %>%
  summarise(N = length(.data[[params$dependent_response_team]]))

GT_tableData %>%
  kable(caption = paste("Data for ", params$Strategy_GT_name_WithSpace)) %>%
  kable_styling()
```

In the `r params$Strategy_GT_name_WithSpace` group, session 4, it looks like there is are a number of teams that have a lt of time remaining. However, I see no obvious pattern.

## Individual

```{r cache=FALSE}
y_label_ind <- "Count"
x_label_ind <- params$dependent_response_name_WithSpace
title_response_ind <- paste("Distribution of", params$dependent_response_name_WithSpace, "(Individual)")
plot_name <- paste("Histogram_", params$dependent_response_name_NoSpace, "_Ind.png", sep = "")
setwd(figure_directory)

plot_data_ind <- ind_data %>%
  select(params$dependent_response_ind, params$dependent_response_DominateStrategy, Target)

ggplot(data = plot_data_ind) + 
  geom_histogram(aes_string(x = params$dependent_response_ind), bins = 40) +
  facet_grid(. ~ .data[[params$dependent_response_DominateStrategy]]) + 
  labs(title = title_response_ind, x = x_label_ind, y = y_label_ind) +
  ggsave(filename = plot_name)
```

Both groups sees to have a distribution that is skewed to the left. The `r params$Strategy_GA_name_WithSpace` group seem to have a large number of outliers but the `r params$Strategy_GT_name_WithSpace` group is more concentrated. 

```{r cache=FALSE}
y_label_ind <- "Count"
x_label_ind <- params$dependent_response_name_WithSpace
title_response_ind <- paste("Distribution of", params$dependent_response_name_WithSpace, "(Individual)")
plot_name <- paste("Histogram_", params$dependent_response_name_NoSpace, "_ByTarget_Ind.png", sep = "")
setwd(figure_directory)

plot_data_ind <- ind_data %>%
  select(params$dependent_response_ind, params$dependent_response_DominateStrategy, Target)

ggplot(data = plot_data_ind) + 
  geom_histogram(aes_string(x = params$dependent_response_ind), bins = 30) +
  facet_grid(.data[[params$dependent_response_DominateStrategy]] ~ Target) +
  labs(title = title_response_ind, x = x_label_ind, y = y_label_ind) +
  ggsave(filename = plot_name)

# Information about the N values in each condition
tableData <- ind_data %>%
  group_by(Target, .data[[params$dependent_response_DominateStrategy]]) %>%
  summarise(N = length(.data[[params$dependent_response_ind]]))

tableData %>%
  kable() %>%
  kable_styling()
```

The distributions when grouped by target and strategy is similar to the overall distribution. 

```{r}
y_label_ind <- "Count"
x_label_ind <- params$dependent_response_name_WithSpace
setwd(figure_directory)

plot_data_ind <- ind_data %>%
  select(params$dependent_response_ind, 
         params$dependent_response_DominateStrategy,
         Target, 
         SessionOrder)

# Generate data by strategy
GA_plot_data_ind <- plot_data_ind %>%
  filter(.data[[params$dependent_response_DominateStrategy]] == params$Strategy_GA_name_WithSpace)

GT_plot_data_ind <- plot_data_ind %>%
  filter(.data[[params$dependent_response_DominateStrategy]] == params$Strategy_GT_name_WithSpace)

# plot
  # GA
ggplot(data = GA_plot_data_ind) + 
  geom_histogram(aes_string(x = params$dependent_response_ind), bins = 30) +
  facet_grid(SessionOrder ~ Target) +
  labs(title = paste("Distribution of", params$dependent_response_name_WithSpace, "(Individual)","(", params$Strategy_GA_name_WithSpace ,")" ), x = x_label_ind, y = y_label_ind) +
  ggsave(filename = paste("Histogram_", params$dependent_response_name_NoSpace, "_ByTarget_BySessionOrder_", params$Strategy_GA_name_NoSpace, "_Ind.png", sep = ""))

    # Information about the N values in each condition
GA_tableData <- GA_plot_data_ind %>%
  select(params$dependent_response_ind, Target, SessionOrder) %>%
  group_by(Target, SessionOrder) %>%
  summarise(N = length(.data[[params$dependent_response_ind]]))

GA_tableData %>%
  kable(caption =  paste("Data for ", params$Strategy_GA_name_WithSpace)) %>%
  kable_styling()

  # GT
ggplot(data = GT_plot_data_ind) + 
  geom_histogram(aes_string(x = params$dependent_response_ind), bins = 30) +
  facet_grid(SessionOrder ~ Target) +
  labs(title = paste("Distribution of", params$dependent_response_name_WithSpace, "(Individual)","(", params$Strategy_GT_name_WithSpace ,")" ), x = x_label_ind, y = y_label_ind) +
  ggsave(filename = paste("Histogram_", params$dependent_response_name_NoSpace, "_ByTarget_BySessionOrder_", params$Strategy_GT_name_NoSpace, "_Ind.png", sep = ""))

# Information about the N values in each condition
GT_tableData <- GT_plot_data_ind %>%
  select(params$dependent_response_ind, Target, SessionOrder) %>%
  group_by(Target, SessionOrder) %>%
  summarise(N = length(.data[[params$dependent_response_ind]]))

GT_tableData %>%
  kable(caption = paste("Data for ", params$Strategy_GT_name_WithSpace)) %>%
  kable_styling()
```

In the `r params$Strategy_GA_name_WithSpace` group, the bulk of time remaining seems only move slightly, if at all, to the right. Where as the distribution of time reamining in the `r params$Strategy_GT_name_WithSpace`seems to flatten over time.

## Summary

Overall, there were no obvious patterns at the team level. At the individual level, when grouped by Target, session order, and `r params$Strategy_GT_name_WithSpace`, the distributions faltten over time, as oppsed to staying the same. The distribution at the individiual level, grouped by target, session order, and `r params$Strategy_GA_name_WithSpace`, seems to change only a little but not much. 

I am getting the sense that strategy may have a significant effect on the time remaining, even if it is small. However, there may not be enough teams to detect the effect. 

























# References