---
title: 'Dissertation Analysis: Familiarity'
author: "Jamiahus Walton"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: true
editor_options:
  chunk_output_type: inline
csl: apa.csl
bibliography: bibliography.bib
---

```{r setup, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Tips for formatting in RMarkdown
# Link: https://monashbioinformaticsplatform.github.io/2017-11-16-open-science-training/topics/rmarkdown.html

# Equations
# Link: https://www.calvin.edu/~rpruim/courses/s341/S17/from-class/MathinRmd.html

# Create awesome HTML table with knitr::kableand kableExtra
# LinkL https://haozhu233.github.io/kableExtra/awesome_table_in_html.html

# Examples of how to use the ggrepel package
# Link: https://cran.r-project.org/web/packages/ggrepel/vignettes/ggrepel.html#examples

# Packages for data analysis
library(tidyverse)
library(lme4)
library(lmerTest)
library(emmeans)
library(svMisc)
library(MuMIn)
library(modelr)
library(sjstats)
library(robustlmm)
library(ggrepel)
library(knitr)
library(kableExtra)

# Functions used in documents ----
remove_measures_with_given_value <- function(data_set, col_name, value){
  rows_to_move <- which(as.vector(data_set[,col_name]) == value) 
  
  return(data_set[-rows_to_move,])
}

# Factor columns that need it.
re_factor_columns <- function(userData, columnNames){
  factorData <- userData
  for(column in columnNames){
    print(column)
    factorData[,column] <- factor(factorData[,column])
  }
  return(factorData)
}

# Model the data for the team level analysis ----
model_data_Target_Session <- function(df, dependent, model.type, is.team, is.robust){
  
  if(is.team){
    if(model.type == "null" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ 1 + (1|Team)")))
    } else if(model.type == "All"){
      lmer(data = df, as.formula(paste(dependent,"~ Target * SessionOrder + (1|Team)")))
    } else if(model.type == "NoInteraction" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ Target + SessionOrder + (1|Team)")))
    } else if(model.type == "NoInteraction_NoTarget" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ SessionOrder + (1|Team)")))
    } else if(model.type == "NoInteraction_NoSession" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ Target + (1|Team)")))
    } else if(model.type == "null" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ 1 + (1|Team)")))
    } else if(model.type == "All" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ Target * SessionOrder + (1|Team)")))
    } else if(model.type == "NoInteraction" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ Target + SessionOrder + (1|Team)")))
    } else if(model.type == "NoInteraction_NoTarget" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ SessionOrder + (1|Team)")))
    } else if(model.type == "NoInteraction_NoSession" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ Target + (1|Team)")))
    } else{
      stop("Model.type not supported")
    }
  } else {
    # Run this code if individual level model
    if(model.type == "null" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ 1 + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "All" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ Target * SessionOrder + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "NoInteraction" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ Target + SessionOrder + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "NoInteraction_NoTarget" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ SessionOrder + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "NoInteraction_NoSession"){
      lmer(data = df, as.formula(paste(dependent,"~ Target + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "null" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ 1 + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "All" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ Target * SessionOrder + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "NoInteraction" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ Target + SessionOrder + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "NoInteraction_NoTarget" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ SessionOrder + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "NoInteraction_NoSession" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ Target + (1|Team) + (1| Player_ID)")))
    } else{
      stop("Model.type not supported")
    }
  }
}

#Folder locations ----
figure_directory <- "C:\\Users\\jamia\\Box\\TMET2\\DATA TMET2\\Data_And_Calcuations\\Figures"
main_work_directory_name <- "C:\\Users\\jamia\\Box\\TMET2\\DATA TMET2\\Data_And_Calcuations\\Raw Data\\"

database_folder_name <- "Database"
file_name_output <- "team_player_aggragate_stats.csv"
folder_location_database <- paste(main_work_directory_name, database_folder_name, sep = "")
aggregate_folder_location <- paste(folder_location_database,"\\", file_name_output, sep = "") #This will combine the final file name and the desiered folder location
familiarity_filename<- "familiarity.csv"

# Read aggregaate data ----
my_aggregate_data <- read.csv(file =  aggregate_folder_location)

clean_aggregate_data_stats <- remove_measures_with_given_value(data_set =  my_aggregate_data, col_name = "Condition", value = "A") # without none condition

# Read familiarity data
my_familiarity_data<- read.csv(file = paste(folder_location_database,"\\",familiarity_filename, sep=""))

# Demographics titles
demo_names <- c("Rand",	
                "Gender_Male_Female_Other_PreferNotToAnswer",
                "age_range",
                "highest_degree",
                "student_status",
                "academic_major",
                "academic_major_other",
                "is_vision_20_20",
                "can_communicate_with_team",
                "can_hold_my_team_back",
                "can_team_slow_me_down",
                "can_teams_perform_better_than_ind",
                "can_feedback_useful_for_teamwork",
                "can_i_learn_better_in_team",
                "can_navigate_VE",
                "video_game_play_frequency",
                "work_in_team_frequency")

# Re factor the columns
columns_to_refactor <- c("SessionOrder", 
                         "Team", 
                         "Player_ID", 
                         "Condition", 
                         "Dominate.Strategy", 
                         "Condition", 
                         "Target",
                         "Confident_team_comm_important_details_quickly",
                         demo_names)
clean_aggregate_data_stats <- re_factor_columns(clean_aggregate_data_stats, columns_to_refactor)

# What is the N for Teams ----
N_teams <- length(levels(factor(clean_aggregate_data_stats$Team)))

# What is the N for Inds ----
N_ind <- length(levels(factor(clean_aggregate_data_stats$Player_ID) ))

# Team data set ----
team_data <- clean_aggregate_data_stats %>%
  filter(Player == 1)

# Individual data set ----
ind_data <- clean_aggregate_data_stats

```

# Motivation

The motivation behind this analysis is to see how familiarity played a role in team performance. 

# Q: What is the familiarity breakdown when data is split by strategy?

## Team

```{r}
N_familiar<- my_familiarity_data[["Familiar"]]
N_Strangers<- my_familiarity_data[["Strangers"]]
N_Partially<- my_familiarity_data[["Partially"]]

my_familiarity_data%>%
  select(Familiarity)%>%
  group_by(Familiarity)%>%
  summarise(count = length(.data[["Familiarity"]]),
            percent = length(.data[["Familiarity"]]) / length(my_familiarity_data[["Familiarity"]]) * 100)
```

Overall, there were 11 familiar teams, 20 partially familiar teams, and 15 teams that were strangers 


```{r}
plot_data_team <- team_data%>%
  select(familiarity, 
         Dominate.Strategy,
         Target) 

ggplot(plot_data_team, aes(x = factor(Dominate.Strategy))) + 
  geom_bar()+
  labs(title= "Strategy count, grouped by team familiarity", x = "Strategy")+
  facet_grid(. ~ familiarity)

plot_data_team %>%
  group_by(familiarity) %>%
  summarise(N = length(.data[["familiarity"]])) %>%
  kable()%>%
  kable_styling()
```

The figure above suggest that teams that were strangers favored Go Alone.

```{r}
plot_data_team <- team_data%>%
  select(familiarity, 
         Dominate.Strategy,
         Target,
         SessionOrder,
         Team) 

ggplot(plot_data_team, aes(x = factor(Dominate.Strategy))) + 
  geom_bar()+
  labs(title= "Strategy count, grouped by team familiarity and session order", x = "Strategy")+
  facet_grid(SessionOrder ~ familiarity)

plot_data_team %>%
  group_by(familiarity, SessionOrder, Dominate.Strategy) %>%
  summarise(N = length(.data[["familiarity"]])) %>%
  kable()%>%
  kable_styling()
```

Familiar and partially teams seems to have similar strategy distrbution. The Stranger teams seem to favor Go Alone. Most Stranger teams used Go Alone at the first session and then gradually began to switch to the Go Tgether.

###Summary
__NEED TO INCLUDE SUMMARY FOR NEW FIGURES__


# Q: Does team familiarity influence the distribution of dependent variables?

## Team

```{r cache=FALSE}
y_label_team <- "Count"
x_label_team <- "Time Remaining"
title_response_team <- paste("Distribution of", "Time Remaining", "(Team)")
plot_name <- paste("Histogram_", "TimeRemaining", "_Team.png", sep = "")
setwd(figure_directory)

plot_data_team <- team_data %>%
  select("timeRemaining_team", 
         familiarity,
         Dominate.Strategy, 
         Target)

ggplot(data = plot_data_team) + 
  geom_histogram(aes_string(x = "timeRemaining_team"), bins = 30) +
  facet_grid( . ~ Dominate.Strategy) +
  labs(title = title_response_team, x = x_label_team, y = y_label_team) +
  ggsave(filename = plot_name)

ggplot(data = plot_data_team) + 
  geom_histogram(aes_string(x = "timeRemaining_team"), bins = 30) +
  facet_grid( familiarity ~ Dominate.Strategy) +
  labs(title = title_response_team, x = x_label_team, y = y_label_team) +
  ggsave(filename = plot_name)
```

I do not see an obvious pattern. The data when grouped by familiarity is similar to the overall distribution of data. 

## Individual

```{r cache=FALSE}
y_label_ind <- "Count"
x_label_ind <- "Time Remaining"
title_response_ind <- paste("Distribution of", "Time Remaining", "(Ind)")
plot_name <- paste("Histogram_", "TimeRemaining", "_ind.png", sep = "")
setwd(figure_directory)

plot_data_ind <- ind_data %>%
  select("timeRemaining_ind", 
         familiarity,
         Dominate.Strategy, 
         Target)

ggplot(data = plot_data_ind) + 
  geom_histogram(aes_string(x = "timeRemaining_ind"), bins = 30) +
  facet_grid( . ~ Dominate.Strategy) +
  labs(title = title_response_ind, x = x_label_ind, y = y_label_ind) +
  ggsave(filename = plot_name)

ggplot(data = plot_data_ind) + 
  geom_histogram(aes_string(x = "timeRemaining_ind"), bins = 30) +
  facet_grid( familiarity ~ Dominate.Strategy) +
  labs(title = title_response_ind, x = x_label_ind, y = y_label_ind) +
  ggsave(filename = plot_name)
```


# NEED TO COMPLETE THIS ANALYSIS














