---
title: 'Dissertation Analysis: Correlations - Collection Rate (Team) - Team Orientation'
author: "Jamiahus Walton"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: true
editor_options:
  chunk_output_type: inline
params:
  dependent_response_name_WithSpace: "Collection Rate"
  dependent_response_name_NoSpace: "CollectionRate"
  dependent_response_team: "Collection_rate_correct_item_team"
---

```{r setup, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Tips for formatting in RMarkdown
# Link: https://monashbioinformaticsplatform.github.io/2017-11-16-open-science-training/topics/rmarkdown.html

# Equations
# Link: https://www.calvin.edu/~rpruim/courses/s341/S17/from-class/MathinRmd.html

# Create awesome HTML table with knitr::kableand kableExtra
# LinkL https://haozhu233.github.io/kableExtra/awesome_table_in_html.html

# Examples of how to use the ggrepel package
# Link: https://cran.r-project.org/web/packages/ggrepel/vignettes/ggrepel.html#examples

# Packages for data analysis
library(tidyverse)
library(lme4)
library(lmerTest)
library(emmeans)
library(svMisc)
library(MuMIn)
library(modelr)
library(sjstats)
library(robustlmm)
library(ggrepel)
library(knitr)
library(kableExtra)

# Functions used in documents ----
remove_measures_with_given_value <- function(data_set, col_name, value){
  rows_to_move <- which(as.vector(data_set[,col_name]) == value) 
  
  return(data_set[-rows_to_move,])
}

# Factor columns that need it.
re_factor_columns <- function(userData, columnNames){
  factorData <- userData
  for(column in columnNames){
    print(column)
    factorData[,column] <- factor(factorData[,column])
  }
  return(factorData)
}

# Model the data for the team level analysis ----
model_data_Target_Session <- function(df, dependent, model.type, is.team, is.robust){
  
  if(is.team){
    if(model.type == "null" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ 1 + (1|Team)")))
    } else if(model.type == "All"){
      lmer(data = df, as.formula(paste(dependent,"~ Target * SessionOrder + (1|Team)")))
    } else if(model.type == "NoInteraction" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ Target + SessionOrder + (1|Team)")))
    } else if(model.type == "NoInteraction_NoTarget" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ SessionOrder + (1|Team)")))
    } else if(model.type == "NoInteraction_NoSession" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ Target + (1|Team)")))
    } else if(model.type == "null" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ 1 + (1|Team)")))
    } else if(model.type == "All" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ Target * SessionOrder + (1|Team)")))
    } else if(model.type == "NoInteraction" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ Target + SessionOrder + (1|Team)")))
    } else if(model.type == "NoInteraction_NoTarget" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ SessionOrder + (1|Team)")))
    } else if(model.type == "NoInteraction_NoSession" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ Target + (1|Team)")))
    } else{
      stop("Model.type not supported")
    }
  } else {
    # Run this code if individual level model
    if(model.type == "null" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ 1 + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "All" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ Target * SessionOrder + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "NoInteraction" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ Target + SessionOrder + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "NoInteraction_NoTarget" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ SessionOrder + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "NoInteraction_NoSession"){
      lmer(data = df, as.formula(paste(dependent,"~ Target + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "null" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ 1 + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "All" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ Target * SessionOrder + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "NoInteraction" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ Target + SessionOrder + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "NoInteraction_NoTarget" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ SessionOrder + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "NoInteraction_NoSession" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ Target + (1|Team) + (1| Player_ID)")))
    } else{
      stop("Model.type not supported")
    }
  }
}

#Folder locations ----
figure_directory <- "C:\\Users\\jamia\\Box\\TMET2\\DATA TMET2\\Data_And_Calcuations\\Figures"
main_work_directory_name <- "C:\\Users\\jamia\\Box\\TMET2\\DATA TMET2\\Data_And_Calcuations\\Raw Data\\"

database_folder_name <- "Database"
file_name_output <- "team_player_aggragate_stats.csv"
folder_location_database <- paste(main_work_directory_name, database_folder_name, sep = "")
aggregate_folder_location <- paste(folder_location_database,"\\", file_name_output, sep = "") #This will combine the final file name and the desiered folder location

# Read aggregaate data ----
my_aggregate_data <- read.csv(file =  aggregate_folder_location)

clean_aggregate_data_stats <- remove_measures_with_given_value(data_set =  my_aggregate_data, col_name = "Condition", value = "A") # without none condition

# Re factor the columns
columns_to_refactor <- c("SessionOrder", 
                         "Team", 
                         "Player_ID", 
                         "Condition", 
                         "Dominate.Strategy", 
                         "Condition", 
                         "Target",
                         "Confident_team_comm_important_details_quickly")
clean_aggregate_data_stats <- re_factor_columns(clean_aggregate_data_stats, columns_to_refactor)

# What is the N for Teams ----
N_teams <- length(levels(factor(clean_aggregate_data_stats$Team)))

# What is the N for Inds ----
N_ind <- length(levels(factor(clean_aggregate_data_stats$Player_ID) ))

# Team data set ----
team_data <- clean_aggregate_data_stats %>%
  filter(Player == 1)

# Individual data set ----
ind_data <- clean_aggregate_data_stats

PostSession_names <- c("NoticeFeedback", 
                       "Feedback_Helpful", 
                       "My_Performance", 
                       "Team_Performance", 
                       "Our_Communication",
                       "P1_can_communi",
                       "P1_performance",
                       "P1_work_with_again",
                       "P2_can_communi",
                       "P2_performance",
                       "P2_work_with_again",
                       "P3_can_communi",
                       "P3_performance",
                       "P3_work_with_again",
                       "Team_perform_well",
                       "Belief_incompatible_with_team",
                       "Member_belief_incompatible_with_other_member",
                       "Confident_team_comm_important_details_quickly",	
                       "Confident_team_comm_important_events",
                       "Confident_team_accurately_assess_handling_information",
                       "Confident_team_quickly_assess_handling_information",
                       "Confident_team_accurately_transfer_information")

# NASA TLX scale names
TLX_Scale_Names <- c("Mental.Demand", "Physical.Demand", "Temporal.Demand", "Performance", "Effort", "Frustration" )
```

# Motivation

The motivation behind this analysis is to discover different correlations between team's actual performance and participants perception of team performance. 

__Note:__ The corect item collection time variaable's units is Sec per item. A high performing team will have a lower value and low performing team will have a higher value. 

# Is there correlation between a actual performance (i.e., `r params$dependent_response_name_WithSpace`) and self-reported performance (i.e, Performance (reverse) from TLX)?

## `r params$dependent_response_name_WithSpace` - `r params$dependent_response_team`

### Plots and Stats

```{r}

plot_data_ind <- ind_data %>%
  select(Team_Performance,
         params$dependent_response_team,
         Target) %>%
  mutate(Team_Performance_f = factor(.data[["Team_Performance"]], levels = c("Very poor", "Poor", "Average", "Good", "Excellent"))) # This mutate column was generated to order the facet groups. 

ggplot(data = plot_data_ind, aes(x = Team_Performance_f, y = .data[[params$dependent_response_team]])) +
  geom_point() +
  facet_grid( . ~ Target)
```

No obious patterns. No obvious violation of monotonic relationship.

```{r}

for (my_target in c("Ind", "Team", "Ind_Team")) {
  plot_data_ind <- ind_data %>%
    select(Team_Performance,
         params$dependent_response_team,
         Target) %>%
    mutate(Team_Performance_f = factor(.data[["Team_Performance"]], levels = c("Very poor", "Poor", "Average", "Good", "Excellent"))) %>% # This mutate column was generated to order the facet groups. This needed because this puts this factor in order from smallest to greatest. I expect a pattern to occur when moving from smallest (1 - Very Poor) to greatest (5 - Excellent)
    filter(Target == my_target)
  
  N_paris<- length(plot_data_ind[[params$dependent_response_team]])
  
  print(paste("Correltation: Condition =", my_target))
  print(paste("Pairs:", N_paris))
  
  print(cor.test(y = plot_data_ind[[params$dependent_response_team]], x = as.numeric(plot_data_ind[["Team_Performance_f"]]), method = "kendall"))
}

```

When grouping paired responses for correct collection rate and performance (reverse) by Target, the results showed a __significant__ negative correlation for Ind ($\tau_b =  -0.278891$), Team($\tau_b =  -0.3282895$), and IaT($\tau_b = -0.2038097$), indicating a correct perception of team performance.

```{r}

plot_data_ind <- ind_data %>%
  select(Team_Performance,
         params$dependent_response_team,
         SessionOrder) %>%
  mutate(Team_Performance_f = factor(.data[["Team_Performance"]], levels = c("Very poor", "Poor", "Average", "Good", "Excellent"))) # This mutate column was generated to order the facet groups. 

ggplot(data = plot_data_ind, aes(x = Team_Performance_f, y = .data[[params$dependent_response_team]])) +
  geom_point() +
  facet_grid( . ~ SessionOrder)
```

No obvious violation of monotonic relationship.

```{r}

for (my_session in c(2:4)) {
  plot_data_ind <- ind_data %>%
    select(Team_Performance,
           params$dependent_response_team,
           SessionOrder) %>%
    mutate(Team_Performance_f = factor(.data[["Team_Performance"]], levels = c("Very poor", "Poor", "Average", "Good", "Excellent"))) %>% # This mutate column was generated to order the facet groups. 
    filter(SessionOrder == my_session)
  
  N_paris<- length(plot_data_ind[[params$dependent_response_team]])
  
  print(paste("Correltation: Session =", my_session))
  print(paste("Pairs:", N_paris))
  
  print(cor.test(y = plot_data_ind[[params$dependent_response_team]], x = as.numeric(plot_data_ind[["Team_Performance_f"]]), method = "kendall"))
}
```

When grouping paired responses for correct collection rate and performance (reverse) by session order, the results showed a __significant__ negative correlation in session 3 ($\tau_b = -0.2662358  $) and 4 ($\tau_b =  -0.3303187$).

```{r}
plot_data_ind <- ind_data %>%
  select(Team_Performance,
         params$dependent_response_team,
         Target,
         SessionOrder) %>%
  mutate(Team_Performance_f = factor(.data[["Team_Performance"]], levels = c("Very poor", "Poor", "Average", "Good", "Excellent"))) # This mutate column was generated to order the facet groups. 

ggplot(data = plot_data_ind, aes(x = Team_Performance_f, y = .data[[params$dependent_response_team]])) +
  geom_point() +
  facet_grid( Target ~ SessionOrder)
```

No obvious violation of monotonic relationship.

```{r}
for (my_session in c(2:4)) {
  for (my_target in c("Ind", "Team", "Ind_Team")) {
    plot_data_ind <- ind_data %>%
      select(Team_Performance,
             params$dependent_response_team,
             Target,
             SessionOrder) %>%
      mutate(Team_Performance_f = factor(.data[["Team_Performance"]], levels = c("Very poor", "Poor", "Average", "Good", "Excellent"))) %>% # This mutate column was generated to order the facet groups. 
      filter(Target == my_target, SessionOrder == my_session)
    
    N_paris<- length(plot_data_ind[[params$dependent_response_team]])
    
    test<- cor.test(y = plot_data_ind[[params$dependent_response_team]], x = as.numeric(plot_data_ind[["Team_Performance_f"]]), method = "kendall")
    
    if(test$p.value < 0.1){
      print(paste("Correltation: Condition =", my_target,",", "Session =", my_session))
      print(paste("Pairs:", N_paris))
    }
    print(test$p.value)
  }
}
```
There was a __significant__ correltation in the following condition and session combinations:
Condition = Ind , Session = 3
Condition = Ind , Session = 4
Condition = Team , Session = 4

There was a __marginally significant__ correlation in the folloing condition and session:
Condition = Team , Session = 2

```{r}
my_target<- "Ind"
my_session<- 3

plot_data_ind <- ind_data %>%
  select(Team_Performance,
         params$dependent_response_team,
         Target,
         SessionOrder) %>%
  mutate(Team_Performance_f = factor(.data[["Team_Performance"]], levels = c("Very poor", "Poor", "Average", "Good", "Excellent"))) %>% # This mutate column was generated to order the facet groups. 
  filter(Target == my_target, SessionOrder == my_session)

N_paris<- length(plot_data_ind[[params$dependent_response_team]])

test<- cor.test(y = plot_data_ind[[params$dependent_response_team]], x = as.numeric(plot_data_ind[["Team_Performance_f"]]), method = "kendall")

if(test$p.value < 0.1){
  print(paste("Correltation: Condition =", my_target,",", "Session =", my_session))
  print(paste("Pairs:", N_paris))
}

print(test)

#----
my_target<- "Ind"
my_session<- 4

plot_data_ind <- ind_data %>%
  select(Team_Performance,
         params$dependent_response_team,
         Target,
         SessionOrder) %>%
  mutate(Team_Performance_f = factor(.data[["Team_Performance"]], levels = c("Very poor", "Poor", "Average", "Good", "Excellent"))) %>% # This mutate column was generated to order the facet groups. 
  filter(Target == my_target, SessionOrder == my_session)

N_paris<- length(plot_data_ind[[params$dependent_response_team]])

test<- cor.test(y = plot_data_ind[[params$dependent_response_team]], x = as.numeric(plot_data_ind[["Team_Performance_f"]]), method = "kendall")

if(test$p.value < 0.1){
  print(paste("Correltation: Condition =", my_target,",", "Session =", my_session))
  print(paste("Pairs:", N_paris))
}

print(test)

#----
my_target<- "Team"
my_session<- 4

plot_data_ind <- ind_data %>%
  select(Team_Performance,
         params$dependent_response_team,
         Target,
         SessionOrder) %>%
  mutate(Team_Performance_f = factor(.data[["Team_Performance"]], levels = c("Very poor", "Poor", "Average", "Good", "Excellent"))) %>% # This mutate column was generated to order the facet groups. 
  filter(Target == my_target, SessionOrder == my_session)

N_paris<- length(plot_data_ind[[params$dependent_response_team]])

test<- cor.test(y = plot_data_ind[[params$dependent_response_team]], x = as.numeric(plot_data_ind[["Team_Performance_f"]]), method = "kendall")

if(test$p.value < 0.1){
  print(paste("Correltation: Condition =", my_target,",", "Session =", my_session))
  print(paste("Pairs:", N_paris))
}

print(test)

#----
my_target<- "Team"
my_session<- 2

plot_data_ind <- ind_data %>%
  select(Team_Performance,
         params$dependent_response_team,
         Target,
         SessionOrder) %>%
  mutate(Team_Performance_f = factor(.data[["Team_Performance"]], levels = c("Very poor", "Poor", "Average", "Good", "Excellent"))) %>% # This mutate column was generated to order the facet groups. 
  filter(Target == my_target, SessionOrder == my_session)

N_paris<- length(plot_data_ind[[params$dependent_response_team]])

test<- cor.test(y = plot_data_ind[[params$dependent_response_team]], x = as.numeric(plot_data_ind[["Team_Performance_f"]]), method = "kendall")

if(test$p.value < 0.1){
  print(paste("Correltation: Condition =", my_target,",", "Session =", my_session))
  print(paste("Pairs:", N_paris))
}

print(test)

```

When grouping paired responses for correct collection rate and performance (reverse) by target and session order, the results showed a __significant__ negative correlation in Ind in session 3 ($\tau_b = -0.5273944$), in Ind in session 4 ($\tau_b = -0.3865452 $), and Team in session 4 ($\tau_b = -0.4506159$). The results showed a __marginally signifcant__ negative correlation in Team in session 2 ($\tau_b = -0.2215666$).


## Summary 

"When grouping paired responses for correct collection rate and performance (reverse) by Target, the results showed a __significant__ negative correlation for Ind ($\tau_b =  -0.278891$), Team($\tau_b =  -0.3282895$), and IaT($\tau_b = -0.2038097$), indicating a correct perception of team performance."

"When grouping paired responses for correct collection rate and performance (reverse) by session order, the results showed a __significant__ negative correlation in session 3 ($\tau_b = -0.2662358  $) and 4 ($\tau_b =  -0.3303187$)."

"When grouping paired responses for correct collection rate and performance (reverse) by target and session order, the results showed a __significant__ negative correlation in Ind in session 3 ($\tau_b = -0.5273944$), in Ind in session 4 ($\tau_b = -0.3865452 $), and Team in session 4 ($\tau_b = -0.4506159$). The results showed a __marginally signifcant__ negative correlation in Team in session 2 ($\tau_b = -0.2215666$)."


 
 































