---
title: 'Dissertation Analysis: Demographics and Strategy'
author: "Jamiahus Walton"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: true
editor_options:
  chunk_output_type: inline
csl: apa.csl
bibliography: bibliography.bib
  
---
```{r setup, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Tips for formatting in RMarkdown
# Link: https://monashbioinformaticsplatform.github.io/2017-11-16-open-science-training/topics/rmarkdown.html

# Equations
# Link: https://www.calvin.edu/~rpruim/courses/s341/S17/from-class/MathinRmd.html

# Create awesome HTML table with knitr::kableand kableExtra
# LinkL https://haozhu233.github.io/kableExtra/awesome_table_in_html.html

# Examples of how to use the ggrepel package
# Link: https://cran.r-project.org/web/packages/ggrepel/vignettes/ggrepel.html#examples

# Packages for data analysis
library(tidyverse)
library(lme4)
library(lmerTest)
library(emmeans)
library(svMisc)
library(MuMIn)
library(modelr)
library(sjstats)
library(robustlmm)
library(ggrepel)
library(knitr)
library(kableExtra)

# Functions used in documents ----
remove_measures_with_given_value <- function(data_set, col_name, value){
  rows_to_move <- which(as.vector(data_set[,col_name]) == value) 
  
  return(data_set[-rows_to_move,])
}

# Factor columns that need it.
re_factor_columns <- function(userData, columnNames){
  factorData <- userData
  for(column in columnNames){
    print(column)
    factorData[,column] <- factor(factorData[,column])
  }
  return(factorData)
}

# Model the data for the team level analysis ----
model_data_Target_Session <- function(df, dependent, model.type, is.team, is.robust){
  
  if(is.team){
    if(model.type == "null" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ 1 + (1|Team)")))
    } else if(model.type == "All"){
      lmer(data = df, as.formula(paste(dependent,"~ Target * SessionOrder + (1|Team)")))
    } else if(model.type == "NoInteraction" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ Target + SessionOrder + (1|Team)")))
    } else if(model.type == "NoInteraction_NoTarget" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ SessionOrder + (1|Team)")))
    } else if(model.type == "NoInteraction_NoSession" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ Target + (1|Team)")))
    } else if(model.type == "null" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ 1 + (1|Team)")))
    } else if(model.type == "All" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ Target * SessionOrder + (1|Team)")))
    } else if(model.type == "NoInteraction" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ Target + SessionOrder + (1|Team)")))
    } else if(model.type == "NoInteraction_NoTarget" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ SessionOrder + (1|Team)")))
    } else if(model.type == "NoInteraction_NoSession" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ Target + (1|Team)")))
    } else{
      stop("Model.type not supported")
    }
  } else {
    # Run this code if individual level model
    if(model.type == "null" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ 1 + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "All" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ Target * SessionOrder + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "NoInteraction" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ Target + SessionOrder + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "NoInteraction_NoTarget" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ SessionOrder + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "NoInteraction_NoSession"){
      lmer(data = df, as.formula(paste(dependent,"~ Target + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "null" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ 1 + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "All" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ Target * SessionOrder + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "NoInteraction" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ Target + SessionOrder + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "NoInteraction_NoTarget" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ SessionOrder + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "NoInteraction_NoSession" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ Target + (1|Team) + (1| Player_ID)")))
    } else{
      stop("Model.type not supported")
    }
  }
}

#Folder locations ----
figure_directory <- "C:\\Users\\jamia\\Box\\TMET2\\DATA TMET2\\Data_And_Calcuations\\Figures"
main_work_directory_name <- "C:\\Users\\jamia\\Box\\TMET2\\DATA TMET2\\Data_And_Calcuations\\Raw Data\\"

database_folder_name <- "Database"
file_name_output <- "team_player_aggragate_stats.csv"
folder_location_database <- paste(main_work_directory_name, database_folder_name, sep = "")
aggregate_folder_location <- paste(folder_location_database,"\\", file_name_output, sep = "") #This will combine the final file name and the desiered folder location

# Read aggregaate data ----
my_aggregate_data <- read.csv(file =  aggregate_folder_location)

clean_aggregate_data_stats <- remove_measures_with_given_value(data_set =  my_aggregate_data, col_name = "Condition", value = "A") # without none condition

# Demographics titles
demo_names <- c("Rand",	
                "Gender_Male_Female_Other_PreferNotToAnswer",
                "age_range",
                "highest_degree",
                "student_status",
                "academic_major",
                "academic_major_other",
                "is_vision_20_20",
                "can_communicate_with_team",
                "can_hold_my_team_back",
                "can_team_slow_me_down",
                "can_teams_perform_better_than_ind",
                "can_feedback_useful_for_teamwork",
                "can_i_learn_better_in_team",
                "can_navigate_VE",
                "video_game_play_frequency",
                "work_in_team_frequency")

# Re factor the columns
columns_to_refactor <- c("SessionOrder", 
                         "Team", 
                         "Player_ID", 
                         "Condition", 
                         "Dominate.Strategy", 
                         "Condition", 
                         "Target",
                         "Confident_team_comm_important_details_quickly",
                         demo_names)
clean_aggregate_data_stats <- re_factor_columns(clean_aggregate_data_stats, columns_to_refactor)

# What is the N for Teams ----
N_teams <- length(levels(factor(clean_aggregate_data_stats$Team)))

# What is the N for Inds ----
N_ind <- length(levels(factor(clean_aggregate_data_stats$Player_ID) ))

# Team data set ----
team_data <- clean_aggregate_data_stats %>%
  filter(Player == 1)

# Individual data set ----
ind_data <- clean_aggregate_data_stats

```

# Motivation

The motivation behind this analyis is to explore behavior (e.g., distance traveled) and characteristics (e.g., demographics or strategies). I want to explore the survey data and see if any of it can help explain the variance in the data.

# Q: Are there similar demographic characterisitcs for teams that use a certain strategy

## Individual

__Note:__ 1 = Strongly Agree, 7 = Strgonly Disagree

```{r cache=FALSE}
demo_names <- c("Gender_Male_Female_Other_PreferNotToAnswer",
                "age_range",
                "highest_degree",
                "student_status",
                "academic_major",
                "can_communicate_with_team",
                "can_hold_my_team_back",
                "can_team_slow_me_down",
                "can_teams_perform_better_than_ind",
                "can_feedback_useful_for_teamwork",
                "can_i_learn_better_in_team",
                "can_navigate_VE",
                "video_game_play_frequency",
                "work_in_team_frequency")

for (name in demo_names) {
  dependent<- name

  y_label_ind <- "Count"
  
  plot_data_ind <- ind_data %>%
    select(.data[[dependent]], Dominate.Strategy, Target, IndividualScore) 
  
  print(
    suppressWarnings( # This warning supressing is needed for because there is a bug that prevents an HTML document to be generated. 
      ggplot(data = plot_data_ind) +
      geom_histogram(aes(x = .data[[dependent]]), stat = "count") +
      facet_grid(Dominate.Strategy ~ .) +
      labs(title = dependent, x = "Dependent", y = y_label_ind) +
      scale_x_discrete(labels = abbreviate)
    )
  )
  
  print(
    suppressWarnings( # This warning supressing is needed for because there is a bug that prevents an HTML document to be generated. 
      ggplot(data = plot_data_ind) +
      geom_histogram(aes(x = .data[[dependent]]), stat = "count") +
      facet_grid(Dominate.Strategy ~ Target) +
      labs(title = dependent, x = "Dependent", y = y_label_ind) +
      scale_x_discrete(labels = abbreviate)
    )
  )
}



```

Overall, I do not see any obvious characterisitcs that show a partern for teams using the differnet strategies.

There is possible patter for the dependent variable __"can_team_slow_me_down"__. The questions asked was the statement was "Team members slow me down". The participants selected a value from a range of "Strongly Agree (1)" to Strongly Disagree (7). It looks like the center of the distribution of answers for teams that used the Go Alone strategy is around 5 (neither agree nor disagree). 

# Q: Are there interesting distributions for self-reported cognitive workload?

## Individual

### Graph for all TLX metrics

```{r}
TLX_Scale_Names <- c("Mental.Demand", "Physical.Demand", "Temporal.Demand", "Performance", "Effort", "Frustration" )
dependent<- "Temporal.Demand"

for (name in TLX_Scale_Names) {
  dependent<- name
  
  y_label_ind <- "Count"
  
  plot_data_ind <- ind_data %>%
  select(TLX_Scale_Names, 
         Dominate.Strategy, 
         Target, 
         SessionOrder)
  plot<- ggplot(data = plot_data_ind) +
    geom_histogram(aes(x = .data[[dependent]]), bins = 30) +
    facet_grid(Dominate.Strategy ~ Target)
  
  print(
    plot
  )
}
```

It looks like there may be a patter in the following workload channels: _Performance, Frustraton, and Effort_. 

I want to fit a model on the data split by strategy. I want to see if a model with no interaction (i.e., only using the session order and target variable) can explain the varience. 

### Performance

#### Go Alone
```{r}
dependent<- "Performance"

plot_data_ind <- ind_data %>%
  select(dependent, 
         Dominate.Strategy, 
         Target, 
         SessionOrder,
         Team,
         Player_ID)

plot_data_GA <-plot_data_ind %>% filter(Dominate.Strategy == "Go Alone")

model.NoInteraction<- model_data_Target_Session(df = plot_data_GA, dependent =  dependent, model.type =  "NoInteraction", is.team = FALSE, is.robust = FALSE)
emmeans(model.NoInteraction, list(pairwise ~ Target),adjust = "tukey") 
```

Statistically, it looks like there is no significant difference between the Target levels in self performance rating for teams that used Go Alone. 

#### Go Together

```{r}
dependent<- "Performance"

plot_data_ind <- ind_data %>%
  select(dependent, 
         Dominate.Strategy, 
         Target, 
         SessionOrder,
         Team,
         Player_ID)

plot_data_GA <-plot_data_ind %>% filter(Dominate.Strategy == "Go Together")

model.NoInteraction<- model_data_Target_Session(df = plot_data_GA, dependent =  dependent, model.type =  "NoInteraction", is.team = FALSE, is.robust = FALSE)
emmeans(model.NoInteraction, list(pairwise ~ Target),adjust = "tukey") 
```

There is no statisitcally significant difference between the conditions. HOwever, it is important to note that there is a __margnially significant result__ between Team and Ind condtions. The difference indicates that participants felt they did better in the Team condition when compared to the Ind condition. 

__Warning/Note__: The model failed to converge


### Frustraton

#### Go Alone

```{r}
dependent<- "Frustration"

plot_data_ind <- ind_data %>%
  select(dependent, 
         Dominate.Strategy, 
         Target, 
         SessionOrder,
         Team,
         Player_ID)

plot_data_GA <-plot_data_ind %>% filter(Dominate.Strategy == "Go Alone")

model.NoInteraction<- model_data_Target_Session(df = plot_data_GA, dependent =  dependent, model.type =  "NoInteraction", is.team = FALSE, is.robust = FALSE)
emmeans(model.NoInteraction, list(pairwise ~ Target),adjust = "tukey") 
```

No statisitcally significant difference among the conditions

#### Go Together

```{r}
dependent<- "Frustration"

plot_data_ind <- ind_data %>%
  select(dependent, 
         Dominate.Strategy, 
         Target, 
         SessionOrder,
         Team,
         Player_ID)

plot_data_GA <-plot_data_ind %>% filter(Dominate.Strategy == "Go Together")

model.NoInteraction<- model_data_Target_Session(df = plot_data_GA, dependent =  dependent, model.type =  "NoInteraction", is.team = FALSE, is.robust = FALSE)
emmeans(model.NoInteraction, list(pairwise ~ Target),adjust = "tukey") 
```

There is a __significant different__ between Ind and Team, and Ind and Ind_Team conditons. The difference indictate frustation is higher in the Ind condition when compared to the Team or the Ind_Team condition. 

### Effort

#### Go Alone

```{r}
dependent<- "Effort"

plot_data_ind <- ind_data %>%
  select(dependent, 
         Dominate.Strategy, 
         Target, 
         SessionOrder,
         Team,
         Player_ID)

plot_data_GA <-plot_data_ind %>% filter(Dominate.Strategy == "Go Alone")

model.NoInteraction<- model_data_Target_Session(df = plot_data_GA, dependent =  dependent, model.type =  "NoInteraction", is.team = FALSE, is.robust = FALSE)
emmeans(model.NoInteraction, list(pairwise ~ Target),adjust = "tukey") 
```

No statistical differences. 

#### Go Together

```{r}
dependent<- "Effort"

plot_data_ind <- ind_data %>%
  select(dependent, 
         Dominate.Strategy, 
         Target, 
         SessionOrder,
         Team,
         Player_ID)

plot_data_GA <-plot_data_ind %>% filter(Dominate.Strategy == "Go Together")

model.NoInteraction<- model_data_Target_Session(df = plot_data_GA, dependent =  dependent, model.type =  "NoInteraction", is.team = FALSE, is.robust = FALSE)
emmeans(model.NoInteraction, list(pairwise ~ Target),adjust = "tukey") 
```

No statistical differences. 

## Summary

Overall, it looks like there is a significant difference with respect to frustrations when teams used the Go Together strategy. Specifically, there was a __significant different__ between Ind and Team, and Ind and Ind_Team conditons. The differences indictated that frustation is higher in the Ind condition when compared to the Team or the Ind_Team condition. There seems to be a stronger difference between Ind and Team, when compared to the difference between Ind and Ind_Team. 















