---
title: 'Dissertation Analysis: Scores'
author: "Jamiahus Walton"
date: "5/15/2019"
output: html_document
editor_options:
  chunk_output_type: inline
csl: apa.csl
bibliography: bibliography.bib
params:
  dependent_response_name_WithSpace: "Score"
  dependent_response_name_NoSpace: "Score"
  dependent_response_team: "TeamScore"
  dependent_response_ind: "IndividualScore"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Tips for formatting in RMarkdown
# Link: https://monashbioinformaticsplatform.github.io/2017-11-16-open-science-training/topics/rmarkdown.html

# Equations
# Link: https://www.calvin.edu/~rpruim/courses/s341/S17/from-class/MathinRmd.html

# Create awesome HTML table with knitr::kableand kableExtra
# LinkL https://haozhu233.github.io/kableExtra/awesome_table_in_html.html

# Examples of how to use the ggrepel package
# Link: https://cran.r-project.org/web/packages/ggrepel/vignettes/ggrepel.html#examples

# Packages for data analysis
library(tidyverse)
library(lme4)
library(lmerTest)
library(emmeans)
library(svMisc)
library(MuMIn)
library(modelr)
library(sjstats)
library(robustlmm)
library(ggrepel)
library(knitr)
library(kableExtra)

# Functions used in documents ----
remove_measures_with_given_value <- function(data_set, col_name, value){
  rows_to_move <- which(as.vector(data_set[,col_name]) == value) 
  
  return(data_set[-rows_to_move,])
}

# Factor columns that need it.
re_factor_columns <- function(userData, columnNames){
  factorData <- userData
  for(column in columnNames){
    print(column)
    factorData[,column] <- factor(factorData[,column])
  }
  return(factorData)
}

# Model the data for the team level analysis ----
model_data_Target_Session <- function(df, dependent, model.type, is.team, is.robust){
  
  if(is.team){
    if(model.type == "null" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ 1 + (1|Team)")))
    } else if(model.type == "All"){
      lmer(data = df, as.formula(paste(dependent,"~ Target * SessionOrder + (1|Team)")))
    } else if(model.type == "NoInteraction" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ Target + SessionOrder + (1|Team)")))
    } else if(model.type == "NoInteraction_NoTarget" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ SessionOrder + (1|Team)")))
    } else if(model.type == "NoInteraction_NoSession" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ Target + (1|Team)")))
    } else if(model.type == "null" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ 1 + (1|Team)")))
    } else if(model.type == "All" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ Target * SessionOrder + (1|Team)")))
    } else if(model.type == "NoInteraction" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ Target + SessionOrder + (1|Team)")))
    } else if(model.type == "NoInteraction_NoTarget" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ SessionOrder + (1|Team)")))
    } else if(model.type == "NoInteraction_NoSession" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ Target + (1|Team)")))
    } else{
      stop("Model.type not supported")
    }
  } else {
    # Run this code if individual level model
    if(model.type == "null" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ 1 + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "All" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ Target * SessionOrder + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "NoInteraction" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ Target + SessionOrder + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "NoInteraction_NoTarget" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ SessionOrder + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "NoInteraction_NoSession"){
      lmer(data = df, as.formula(paste(dependent,"~ Target + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "null" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ 1 + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "All" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ Target * SessionOrder + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "NoInteraction" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ Target + SessionOrder + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "NoInteraction_NoTarget" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ SessionOrder + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "NoInteraction_NoSession" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ Target + (1|Team) + (1| Player_ID)")))
    } else{
      stop("Model.type not supported")
    }
  }
}

#Folder locations ----
figure_directory <- "C:\\Users\\jamia\\Box\\TMET2\\DATA TMET2\\Data_And_Calcuations\\Figures"
main_work_directory_name <- "C:\\Users\\jamia\\Box\\TMET2\\DATA TMET2\\Data_And_Calcuations\\Raw Data\\"

database_folder_name <- "Database"
file_name_output <- "team_player_aggragate_stats.csv"
folder_location_database <- paste(main_work_directory_name, database_folder_name, sep = "")
aggregate_folder_location <- paste(folder_location_database,"\\", file_name_output, sep = "") #This will combine the final file name and the desiered folder location

# Read aggregaate data ----
my_aggregate_data <- read.csv(file =  aggregate_folder_location)

clean_aggregate_data_stats <- remove_measures_with_given_value(data_set =  my_aggregate_data, col_name = "Condition", value = "A") # without none condition

# Re factor the columns
columns_to_refactor <- c("SessionOrder", 
                         "Team", 
                         "Player_ID", 
                         "Condition", 
                         "Dominate.Strategy", 
                         "Condition", 
                         "Target",
                         "Confident_team_comm_important_details_quickly")
clean_aggregate_data_stats <- re_factor_columns(clean_aggregate_data_stats, columns_to_refactor)

# What is the N for Teams ----
N_teams <- length(levels(factor(clean_aggregate_data_stats$Team)))

# What is the N for Inds ----
N_ind <- length(levels(factor(clean_aggregate_data_stats$Player_ID) ))

# Team data set ----
team_data <- clean_aggregate_data_stats %>%
  filter(Player == 1)

# Individual data set ----
ind_data <- clean_aggregate_data_stats

```

## Purpose

The purpose of this document is to record the data analysis for my Dissertation.

## Experimental Design

This experiment is a within-subject experimental design. The primary variable was the feedback condition (i.e., Target). There were four feedback conditions; None, Individual, Team, and Ind_Team Each team experienced each condition. The first condition for each group was the None condition. The remaining three conditions were counterbalanced. For example, the condition order for team 7 is the following: None, Ind, Team, Ind_Team. The condition order for group 8 is the following: None, Team, Individual, Ind_Team. 

## Data Description

I collected data from **`r N_ind`** participants that formed **`r N_teams`** teams. Below is a sample of the data for the main metrics

```{r main_metrics_table, echo=FALSE}
dt <- clean_aggregate_data_stats[1:5,c("TeamScore", 
                           "IndividualScore", 
                           "CI_team", 
                           "CI_ind", 
                           "II_team", 
                           "II_ind", 
                           "ERROR_team_unique", 
                           "ERROR_ind_unique", 
                           "ERROR_team_total",
                           "ERROR_ind_total")] 
dt %>%
  kable() %>%
  kable_styling()
```

## Research Question

This research attempts to answer the following question: *How will teams' performance change if given feedback that displays indicators based on individual performance, team performance, or both?*

## Exploratory Data Analysis

In this section, I seek to visually discover answers to the research question mentioned above.

### Q: Is there exciting variation among the _`r params$dependent_response_name_WithSpace`_ metric that will help me understand the influence of the feedback condition?

#### Team

```{r hist_CountVSTimeRemaining}
y_label_team <- "Count"
x_label_team <- params$dependent_response_name_WithSpace
title_response_team <- paste("Distribution of", params$dependent_response_name_WithSpace, "(Team)")
plot_name <- paste("Histogram_", params$dependent_response_name_NoSpace, "_Team.png", sep = "")
setwd(figure_directory)

plot_data_team <- team_data %>%
  select(params$dependent_response_team, Target)

ggplot(data = plot_data_team) + 
  geom_histogram(aes_string(x = params$dependent_response_team), bins = 30) +
  labs(title = title_response_team, x = x_label_team, y = y_label_team) +
  ggsave(filename = plot_name)
```



```{r}
y_label_team <- "Count"
x_label_team <- "Target"
title_response_team <- paste("Distribution of", params$dependent_response_name_WithSpace, "(Team)")
plot_name <- paste("Histogram_", params$dependent_response_name_NoSpace, "_ByTarget_Team.png", sep = "")
setwd(figure_directory)

plot_data_team <- team_data %>%
  select(params$dependent_response_team, Target)

ggplot(data = plot_data_team) + 
  geom_histogram(aes_string(x = params$dependent_response_team), bins = 25) +
  facet_grid(. ~ Target) +
  labs(title = title_response_team, x = x_label_team, y = y_label_team) +
  ggsave(filename = plot_name)

# Information about the N values in each condition
tableData <- team_data %>%
  group_by(Target) %>%
  summarise(N = length(.data[[params$dependent_response_team]]))

tableData %>%
  kable() %>%
  kable_styling()
```




#### Individual

```{r}
y_label_ind <- "Count"
x_label_ind <- params$dependent_response_name_WithSpace
title_response_ind <- paste("Distribution of", params$dependent_response_name_WithSpace, "(Individual)")
plot_name <- paste("Histogram_", params$dependent_response_name_NoSpace, "_Ind.png", sep = "")
setwd(figure_directory)

plot_data_ind <- ind_data %>%
  select(params$dependent_response_ind, Target)

ggplot(data = plot_data_ind) + 
  geom_histogram(aes_string(x = params$dependent_response_ind), bins = 40) +
  labs(title = title_response_ind, x = x_label_ind, y = y_label_ind) +
  ggsave(filename = plot_name)
```



```{r}
y_label_ind <- "Count"
x_label_ind <- params$dependent_response_name_WithSpace
title_response_ind <- paste("Distribution of", params$dependent_response_name_WithSpace, "(Individual)")
plot_name <- paste("Histogram_", params$dependent_response_name_NoSpace, "_ByTarget_Ind.png", sep = "")
setwd(figure_directory)

plot_data_ind <- ind_data %>%
  select(params$dependent_response_ind, Target)

ggplot(data = plot_data_ind) + 
  geom_histogram(aes_string(x = params$dependent_response_ind), bins = 30) +
  facet_grid(. ~ Target) +
  labs(title = title_response_ind, x = x_label_ind, y = y_label_ind) +
  ggsave(filename = plot_name)

# Information about the N values in each condition
tableData <- ind_data %>%
  group_by(Target) %>%
  summarise(N = length(.data[[params$dependent_response_ind]]))

tableData %>%
  kable() %>%
  kable_styling()
```

 
  
  
#### Summary / Reflection



### Q: Is there exciting variation among the _`r params$dependent_response_name_WithSpace`_ that explains how the feedback conditions influence the _`r params$dependent_response_name_WithSpace`_ when session order is taken into consideration?

#### Team

```{r}
y_label_team <- "Count"
x_label_team <- params$dependent_response_name_WithSpace
title_response_team <- paste("Distribution of", params$dependent_response_name_WithSpace, "(Team)")
plot_name <- paste("Histogram_", params$dependent_response_name_NoSpace, "_ByTarget_BySessionOrder_Team.png", sep = "")
setwd(figure_directory)

plot_data_team <- team_data %>%
  select(params$dependent_response_team, Target, SessionOrder)

ggplot(data = plot_data_team) + 
  geom_histogram(aes_string(x = params$dependent_response_team), bins = 30) +
  labs(title = title_response_team, x = x_label_team, y = y_label_team) +
  facet_grid( SessionOrder ~ Target) + 
  ggsave(filename = plot_name)

# Information about the N values in each condition
tableData <- team_data %>%
  select(params$dependent_response_team, Target, SessionOrder) %>%
  group_by(Target, SessionOrder) %>%
  summarise(N = length(.data[[params$dependent_response_team]]))

tableData %>%
  kable() %>%
  kable_styling()
```



#### Individual

```{r}
y_label_ind <- "Count"
x_label_ind <- params$dependent_response_name_WithSpace
title_response_ind <- paste("Distribution of", params$dependent_response_name_WithSpace, "(Individual)")
plot_name <- paste("Histogram_", params$dependent_response_name_NoSpace, "_ByTarget_BySessionOrder_Ind.png", sep = "")
setwd(figure_directory)

plot_data_ind <- ind_data %>%
  select(params$dependent_response_ind, Target, SessionOrder)

ggplot(data = plot_data_ind) + 
  geom_histogram(aes_string(x = params$dependent_response_ind), bins = 30) +
  facet_grid(SessionOrder ~ Target) +
  labs(title = title_response_ind, x = x_label_ind, y = y_label_ind) +
  ggsave(filename = plot_name)

# Information about the N values in each condition
tableData <- ind_data %>%
  select(params$dependent_response_ind, Target, SessionOrder) %>%
  group_by(Target, SessionOrder) %>%
  summarise(N = length(.data[[params$dependent_response_ind]]))

tableData %>%
  kable() %>%
  kable_styling()
```




#### Summary / Reflection

















# References