---
title: 'Dissertation Analysis: Correlations - Collection Rate - Team Orientation'
author: "Jamiahus Walton"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: true
editor_options:
  chunk_output_type: inline
params:
  dependent_response_name_WithSpace: "Collection Rate"
  dependent_response_name_NoSpace: "CollectionRate"
  dependent_response_team: "Collection_rate_correct_item_team"
  dependent_response_ind: "Collection_rate_correct_item_ind"
---

```{r setup, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Tips for formatting in RMarkdown
# Link: https://monashbioinformaticsplatform.github.io/2017-11-16-open-science-training/topics/rmarkdown.html

# Equations
# Link: https://www.calvin.edu/~rpruim/courses/s341/S17/from-class/MathinRmd.html

# Create awesome HTML table with knitr::kableand kableExtra
# LinkL https://haozhu233.github.io/kableExtra/awesome_table_in_html.html

# Examples of how to use the ggrepel package
# Link: https://cran.r-project.org/web/packages/ggrepel/vignettes/ggrepel.html#examples

# Packages for data analysis
library(tidyverse)
library(lme4)
library(lmerTest)
library(emmeans)
library(svMisc)
library(MuMIn)
library(modelr)
library(sjstats)
library(robustlmm)
library(ggrepel)
library(knitr)
library(kableExtra)

# Functions used in documents ----
remove_measures_with_given_value <- function(data_set, col_name, value){
  rows_to_move <- which(as.vector(data_set[,col_name]) == value) 
  
  return(data_set[-rows_to_move,])
}

# Factor columns that need it.
re_factor_columns <- function(userData, columnNames){
  factorData <- userData
  for(column in columnNames){
    print(column)
    factorData[,column] <- factor(factorData[,column])
  }
  return(factorData)
}

# Model the data for the team level analysis ----
model_data_Target_Session <- function(df, dependent, model.type, is.team, is.robust){
  
  if(is.team){
    if(model.type == "null" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ 1 + (1|Team)")))
    } else if(model.type == "All"){
      lmer(data = df, as.formula(paste(dependent,"~ Target * SessionOrder + (1|Team)")))
    } else if(model.type == "NoInteraction" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ Target + SessionOrder + (1|Team)")))
    } else if(model.type == "NoInteraction_NoTarget" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ SessionOrder + (1|Team)")))
    } else if(model.type == "NoInteraction_NoSession" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ Target + (1|Team)")))
    } else if(model.type == "null" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ 1 + (1|Team)")))
    } else if(model.type == "All" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ Target * SessionOrder + (1|Team)")))
    } else if(model.type == "NoInteraction" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ Target + SessionOrder + (1|Team)")))
    } else if(model.type == "NoInteraction_NoTarget" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ SessionOrder + (1|Team)")))
    } else if(model.type == "NoInteraction_NoSession" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ Target + (1|Team)")))
    } else{
      stop("Model.type not supported")
    }
  } else {
    # Run this code if individual level model
    if(model.type == "null" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ 1 + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "All" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ Target * SessionOrder + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "NoInteraction" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ Target + SessionOrder + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "NoInteraction_NoTarget" && !is.robust){
      lmer(data = df, as.formula(paste(dependent,"~ SessionOrder + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "NoInteraction_NoSession"){
      lmer(data = df, as.formula(paste(dependent,"~ Target + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "null" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ 1 + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "All" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ Target * SessionOrder + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "NoInteraction" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ Target + SessionOrder + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "NoInteraction_NoTarget" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ SessionOrder + (1|Team) + (1| Player_ID)")))
    } else if(model.type == "NoInteraction_NoSession" && is.robust){
      rlmer(data = df, as.formula(paste(dependent,"~ Target + (1|Team) + (1| Player_ID)")))
    } else{
      stop("Model.type not supported")
    }
  }
}

#Folder locations ----
figure_directory <- "C:\\Users\\jamia\\Box\\TMET2\\DATA TMET2\\Data_And_Calcuations\\Figures"
main_work_directory_name <- "C:\\Users\\jamia\\Box\\TMET2\\DATA TMET2\\Data_And_Calcuations\\Raw Data\\"

database_folder_name <- "Database"
file_name_output <- "team_player_aggragate_stats.csv"
folder_location_database <- paste(main_work_directory_name, database_folder_name, sep = "")
aggregate_folder_location <- paste(folder_location_database,"\\", file_name_output, sep = "") #This will combine the final file name and the desiered folder location

# Read aggregaate data ----
my_aggregate_data <- read.csv(file =  aggregate_folder_location)

clean_aggregate_data_stats <- remove_measures_with_given_value(data_set =  my_aggregate_data, col_name = "Condition", value = "A") # without none condition

# Re factor the columns
columns_to_refactor <- c("SessionOrder", 
                         "Team", 
                         "Player_ID", 
                         "Condition", 
                         "Dominate.Strategy", 
                         "Condition", 
                         "Target",
                         "Confident_team_comm_important_details_quickly")
clean_aggregate_data_stats <- re_factor_columns(clean_aggregate_data_stats, columns_to_refactor)

# What is the N for Teams ----
N_teams <- length(levels(factor(clean_aggregate_data_stats$Team)))

# What is the N for Inds ----
N_ind <- length(levels(factor(clean_aggregate_data_stats$Player_ID) ))

# Team data set ----
team_data <- clean_aggregate_data_stats %>%
  filter(Player == 1)

# Individual data set ----
ind_data <- clean_aggregate_data_stats

PostSession_names <- c("NoticeFeedback", 
                       "Feedback_Helpful", 
                       "My_Performance", 
                       "Team_Performance", 
                       "Our_Communication",
                       "P1_can_communi",
                       "P1_performance",
                       "P1_work_with_again",
                       "P2_can_communi",
                       "P2_performance",
                       "P2_work_with_again",
                       "P3_can_communi",
                       "P3_performance",
                       "P3_work_with_again",
                       "Team_perform_well",
                       "Belief_incompatible_with_team",
                       "Member_belief_incompatible_with_other_member",
                       "Confident_team_comm_important_details_quickly",	
                       "Confident_team_comm_important_events",
                       "Confident_team_accurately_assess_handling_information",
                       "Confident_team_quickly_assess_handling_information",
                       "Confident_team_accurately_transfer_information")

# NASA TLX scale names
TLX_Scale_Names <- c("Mental.Demand", "Physical.Demand", "Temporal.Demand", "Performance", "Effort", "Frustration" )
```

# Motivation

The motivation behind this analysis is to discover different correlations between participants actual performance and self-reported performance. Significance was found in previous analysis regarding a sinificant difference in correct collection rate at the individual level and the goal of this analysis is to attempt to understand why there was significance. 

__Note:__ In TLX, a value of 0 for the performance channel is considered perfect and 100 is considered faile. This is because if you felt the you're performance was perfect, then that would mean your task load was lower. For this analysis, performance was reverse coded so that 0 is failure and 100 is perfect. 

__Note:__ A lower collection rate value indicates a high performaing team. Units for the dependent variable are Sec per Item. 

# Is there correlation between a actual performance (i.e., `r params$dependent_response_name_WithSpace`) and self-reported performance (i.e, Performance (reverse) from TLX)?

## `r params$dependent_response_name_WithSpace` - `r params$dependent_response_ind`

### Plots and Stats

```{r}
# dependent<- "timeRemaining_ind"

plot_data_ind <- ind_data %>%
  select(Performance,
         params$dependent_response_ind,
         Target) %>%
  mutate(performance_reverse = 100 - Performance)

ggplot(data = plot_data_ind, aes(x = performance_reverse, y = .data[[params$dependent_response_ind]])) +
  geom_point() +
  facet_grid( . ~ Target)
```

No obious patterns. No obvious violation of monotonic relationship.

```{r}
# dependent<- "timeRemaining_ind"


for (my_target in c("Ind", "Team", "Ind_Team")) {
  
  plot_data_ind <- ind_data %>%
  select(Performance,
         params$dependent_response_ind,
         SessionOrder,
         Dominate.Strategy,
         My_Performance,
         Target,
         Player_ID) %>%
  mutate(performance_reverse = 100 - Performance) %>%
  filter(Target == my_target)
  
  print(paste("Correltation: Condition =", my_target))
  
  print(cor.test(y = plot_data_ind[[params$dependent_response_ind]], x = plot_data_ind[["performance_reverse"]], method = "spearman"))
  }
```

When grouping paired responses for correct collection rate and performance (reverse) by Target, the results show a __significant__ negative correltation for the Team condition. Indicating correct self perception of performance. Results also show a __marginally significant__ negative correlation in the Ind_Team condition. 

```{r}
# dependent<- "timeRemaining_ind"

plot_data_ind <- ind_data %>%
  select(Performance,
         params$dependent_response_ind,
         SessionOrder)%>%
  mutate(performance_reverse = 100 - Performance)

ggplot(data = plot_data_ind, aes(x = performance_reverse, y = .data[[params$dependent_response_ind]])) +
  geom_point() +
  facet_grid( . ~ SessionOrder)
```

No obvious violation of monotonic relationship.

```{r}

for (my_session in c(2:4)) {
  
  plot_data_ind <- ind_data %>%
  select(Performance,
         params$dependent_response_ind,
         SessionOrder) %>%
  mutate(performance_reverse = 100 - Performance) %>%
  filter(SessionOrder == my_session)
  
  print(paste("Correltation: Session =", my_session))
  
  print(cor.test(y = plot_data_ind[[params$dependent_response_ind]], x = plot_data_ind[["performance_reverse"]], method = "spearman"))
  }
```

When grouping paired responses for correct collection rate and performance (reverse) by session order, the results show a __significant__ negative correlation for session 4. Indicating a correct perception of performance. The results also showed a __marginally significant__ negative correlation in session 2.

```{r}
# dependent<- "timeRemaining_ind"

plot_data_ind <- ind_data %>%
  select(Performance,
         params$dependent_response_ind,
         Target,
         SessionOrder)%>%
  mutate(performance_reverse = 100 - Performance)

ggplot(data = plot_data_ind, aes(x = performance_reverse, y = .data[[params$dependent_response_ind]])) +
  geom_point() +
  facet_grid( Target ~ SessionOrder)
```

No obvious violation of monotonic relationship.

```{r}

for (my_session in c(2:4)) {
  for (my_target in c("Ind", "Team", "Ind_Team")) {
    plot_data_ind <- ind_data %>%
      select(Performance,
             params$dependent_response_ind,
             SessionOrder,
             Target) %>%
      mutate(performance_reverse = 100 - Performance) %>%
      filter(Target == my_target, SessionOrder == my_session)
  
  test<- cor.test(y = plot_data_ind[[params$dependent_response_ind]], x = plot_data_ind[["performance_reverse"]], method = "spearman")
  
  if(test$p.value < 0.1){
    print(paste("Correltation: Condition =", my_target,",", "Session =", my_session))
  }
  print(test$p.value)
  }
}
```

There was a __significant__ correltation in the following condition and session combinations:
Condition = Team , Session = 2
Condition = Ind_Team , Session = 4

```{r}
my_target<- "Team"
my_session<- 2

plot_data_ind <- ind_data %>%
      select(Performance,
             params$dependent_response_ind,
             SessionOrder,
             Target) %>%
      mutate(performance_reverse = 100 - Performance) %>%
      filter(Target == my_target, SessionOrder == my_session)

print(paste("Correltation: Condition =", my_target,",", "Session =", my_session))

test<- cor.test(y = plot_data_ind[[params$dependent_response_ind]], x = plot_data_ind[["performance_reverse"]], method = "spearman")

print(test)

#----

my_target<- "Ind_Team"
my_session<- 4

plot_data_ind <- ind_data %>%
      select(Performance,
             params$dependent_response_ind,
             SessionOrder,
             Target) %>%
      mutate(performance_reverse = 100 - Performance) %>%
      filter(Target == my_target, SessionOrder == my_session)

print(paste("Correltation: Condition =", my_target,",", "Session =", my_session))

test<- cor.test(y = plot_data_ind[[params$dependent_response_ind]], x = plot_data_ind[["performance_reverse"]], method = "spearman")

print(test)
  
```

There was a __significant__ correltation in the following condition and session combinations:
Condition = Team , Session = 2
Condition = Ind_Team , Session = 4

When grouping paired responses for correct collection rate and performance (reverse) by target and session order, the results showed a __significant__ negative correlation for participants in Team in session 2, and for pariticpants in Ind_Team in session 4, indicating a correct perception. 

```{r}
# dependent <- "timeRemaining_ind"
plot_data_ind <- ind_data %>%
  select(Performance,
         params$dependent_response_ind,
         My_Performance) %>%
  mutate(performance_reverse = 100 - Performance) %>%
  mutate(My_Performance_f = factor(.data[["My_Performance"]], levels = c("Excellent", "Good", "Average", "Poor", "Very poor"))) # This mutate column was generated to order the facet groups. 

ggplot(data = plot_data_ind, aes(x = performance_reverse, y = .data[[params$dependent_response_ind]])) +
  geom_point() + 
  facet_grid(. ~ My_Performance_f)
```

No obvious violation of monotonic relationship.

```{r}
for (ind_rating in c("Excellent", "Good", "Average", "Poor", "Very poor")) {
  plot_data_ind <- ind_data %>%
        select(Performance,
               params$dependent_response_ind,
               My_Performance) %>%
        mutate(performance_reverse = 100 - Performance)%>% 
        filter(My_Performance == ind_rating)
  
  print(paste("Correltation: My_rating =", ind_rating))
  
  test<- cor.test(y = plot_data_ind[[params$dependent_response_ind]], x = plot_data_ind[["performance_reverse"]], method = "spearman")
  
  print(test)
}
```

When grouping paired responses for correct collection rate and performance (reverse) by self reported performance (e.g., poor vs. excellent), the results show a __significant__ negative correlation for participants that rated their performance as Excellent, indicating a correct perception of performance. The results also showed a __singnificant__ positive correlation for participants that rated their performance as Poor, indiciating an incorrect perception of performance.

```{r}
# dependent<- "timeRemaining_ind"

plot_data_ind <- ind_data %>%
  select(Performance,
         params$dependent_response_ind,
         My_Performance,
         Target) %>%
  mutate(performance_reverse = 100 - Performance)%>%
  mutate(My_Performance_f = factor(.data[["My_Performance"]], levels = c("Excellent", "Good", "Average", "Poor", "Very poor"))) # This mutate column was generated to order the facet groups. 

ggplot(data = plot_data_ind, aes(x = performance_reverse, y = .data[[params$dependent_response_ind]])) +
  geom_point() +
  facet_grid(My_Performance_f ~ Target)
```

No obvious violation of monotonic relationship.

```{r}

for (ind_rating in c("Excellent", "Good", "Average", "Poor", "Very poor")) {
  for (my_target in c("Ind", "Team", "Ind_Team")) {
    plot_data_ind <- ind_data %>%
        select(Performance,
               params$dependent_response_ind,
               My_Performance,
               Target) %>%
        mutate(performance_reverse = 100 - Performance)%>% 
        filter(My_Performance == ind_rating, Target == my_target)
  
    test<- cor.test(y = plot_data_ind[[params$dependent_response_ind]], x = plot_data_ind[["performance_reverse"]], method = "spearman")
  
    if(test$p.value < 0.1){
      print(paste("Correltation: Condition =", my_target, ", Rated_performance =", ind_rating))
    }
    print(test$p.value)
  }
}
```
The following show a __marginally significant__ correlation:
Condition = Team , Rated_performance = Poor
Condition = Ind_Team , Rated_performance = Poor

```{r}
ind_rating<- "Poor"
my_target<- "Team"
plot_data_ind <- ind_data %>%
        select(Performance,
               params$dependent_response_ind,
               My_Performance,
               Target) %>%
        mutate(performance_reverse = 100 - Performance)%>% 
        filter(My_Performance == ind_rating, Target == my_target)
  
    test<- cor.test(y = plot_data_ind[[params$dependent_response_ind]], x = plot_data_ind[["performance_reverse"]], method = "spearman")
  
    print(paste("Correltation: Condition =", my_target, ", Rated_performance =", ind_rating))
    print(test)
    
#----
ind_rating<- "Poor"
my_target<- "Ind_Team"
plot_data_ind <- ind_data %>%
        select(Performance,
               params$dependent_response_ind,
               My_Performance,
               Target) %>%
        mutate(performance_reverse = 100 - Performance)%>% 
        filter(My_Performance == ind_rating, Target == my_target)
  
    test<- cor.test(y = plot_data_ind[[params$dependent_response_ind]], x = plot_data_ind[["performance_reverse"]], method = "spearman")
  
    print(paste("Correltation: Condition =", my_target, ", Rated_performance =", ind_rating))
    print(test)

```
The following show a __marginally significant__ correlation:
Condition = Team , Rated_performance = Poor
Condition = Ind_Team , Rated_performance = Poor

__Note:__ There are very few participants that rated their performance as poor in the Team and Ind_Team conditions

```{r}
# dependent<- "timeRemaining_ind"

plot_data_ind <- ind_data %>%
  select(Performance,
         params$dependent_response_ind,
         My_Performance,
         SessionOrder) %>%
  mutate(performance_reverse = 100 - Performance)%>%
  mutate(My_Performance_f = factor(.data[["My_Performance"]], levels = c("Excellent", "Good", "Average", "Poor", "Very poor"))) # This mutate column was generated to order the facet groups. 

ggplot(data = plot_data_ind, aes(x = performance_reverse, y = .data[[params$dependent_response_ind]])) +
  geom_point() +
  facet_grid(My_Performance_f ~ SessionOrder)
```

No obvious violation of monotonic relationship.

```{r}
for (ind_rating in c("Excellent", "Good", "Average", "Poor", "Very poor")) {
  for (my_session in c(2:4)) {
    plot_data_ind <- ind_data %>%
        select(Performance,
               params$dependent_response_ind,
               My_Performance,
               SessionOrder) %>%
        mutate(performance_reverse = 100 - Performance)%>% 
        filter(My_Performance == ind_rating, SessionOrder == my_session)
  
    test<- cor.test(y = plot_data_ind[[params$dependent_response_ind]], x = plot_data_ind[["performance_reverse"]], method = "spearman")
  
    if(test$p.value < 0.1){
      print(paste("Correltation: Session =", my_session, ", Rated_performance =", ind_rating))
    }
    print(test$p.value)
  }
}
```

There was a __significant__ correlations for the following: 
Session = 2 , Rated_performance = Excellent
Session = 2 , Rated_performance = Poor

There was a __marginally significant__ correlations for the following: 
Session = 3 , Rated_performance = Poor

```{r}
ind_rating<- "Excellent"
my_session<- 2

plot_data_ind <- ind_data %>%
        select(Performance,
               params$dependent_response_ind,
               My_Performance,
               SessionOrder) %>%
        mutate(performance_reverse = 100 - Performance)%>% 
        filter(My_Performance == ind_rating, SessionOrder == my_session)
  
    test<- cor.test(y = plot_data_ind[[params$dependent_response_ind]], x = plot_data_ind[["performance_reverse"]], method = "spearman")
  
    if(test$p.value < 0.1){
      print(paste("Correltation: Session =", my_session, ", Rated_performance =", ind_rating))
    }
    print(test)
    
#----
ind_rating<- "Poor"
my_session<- 2

plot_data_ind <- ind_data %>%
        select(Performance,
               params$dependent_response_ind,
               My_Performance,
               SessionOrder) %>%
        mutate(performance_reverse = 100 - Performance)%>% 
        filter(My_Performance == ind_rating, SessionOrder == my_session)
  
    test<- cor.test(y = plot_data_ind[[params$dependent_response_ind]], x = plot_data_ind[["performance_reverse"]], method = "spearman")
  
    if(test$p.value < 0.1){
      print(paste("Correltation: Session =", my_session, ", Rated_performance =", ind_rating))
    }
    print(test)
    
```

When grouping paired responses for correct collection rate and performance (reverse) by session order and self reported performance (e.g., poor vs. excellent), the results showed a __significant__ negative correlations for participants in session 2 that rated themsleves as Excellent, indicating a correct perception. The results showed a __significant__ positive correlation for participants in session 2 that rated themselves as Poor, indicating an incorrect perception of performance. 

```{r}
# dependent<- "timeRemaining_ind"
y_lab_indep <- params$dependent_response_name_WithSpace

post_session_labled_performance<- "Excellent"
plot_data_ind <- ind_data %>%
  select(Performance,
         params$dependent_response_ind,
         My_Performance,
         SessionOrder, 
         Target) %>%
  mutate(performance_reverse = 100 - Performance)%>%
  filter(My_Performance == post_session_labled_performance)

ggplot(data = plot_data_ind, aes(x = performance_reverse, y = .data[[params$dependent_response_ind]])) +
  geom_point() +
  labs(title = paste(y_lab_indep, "vs Self-Rated Performance (TLX)"), caption = paste("Participants who label their performance as", post_session_labled_performance) , y = y_lab_indep) +
  facet_grid(SessionOrder ~ Target)

post_session_labled_performance<- "Good"
plot_data_ind <- ind_data %>%
  select(Performance,
         params$dependent_response_ind,
         My_Performance,
         SessionOrder, 
         Target) %>%
  mutate(performance_reverse = 100 - Performance)%>%
  filter(My_Performance == post_session_labled_performance)

ggplot(data = plot_data_ind, aes(x = performance_reverse, y = .data[[params$dependent_response_ind]])) +
  geom_point() +
  labs(title = paste(y_lab_indep, "vs Self-Rated Performance (TLX)"), caption = paste("Participants who label their performance as", post_session_labled_performance) , y = y_lab_indep) +
  facet_grid(SessionOrder ~ Target)

post_session_labled_performance<- "Average"
plot_data_ind <- ind_data %>%
  select(Performance,
         params$dependent_response_ind,
         My_Performance,
         SessionOrder, 
         Target) %>%
  mutate(performance_reverse = 100 - Performance)%>%
  filter(My_Performance == post_session_labled_performance)

ggplot(data = plot_data_ind, aes(x = performance_reverse, y = .data[[params$dependent_response_ind]])) +
  geom_point() +
  labs(title = paste(y_lab_indep, "vs Self-Rated Performance (TLX)"), caption = paste("Participants who label their performance as", post_session_labled_performance) , y = y_lab_indep) +
  facet_grid(SessionOrder ~ Target)

post_session_labled_performance<- "Poor"
plot_data_ind <- ind_data %>%
  select(Performance,
         params$dependent_response_ind,
         My_Performance,
         SessionOrder, 
         Target) %>%
  mutate(performance_reverse = 100 - Performance)%>%
  filter(My_Performance == post_session_labled_performance)

ggplot(data = plot_data_ind, aes(x = performance_reverse, y = .data[[params$dependent_response_ind]])) +
  geom_point() +
  labs(title = paste(y_lab_indep, "vs Self-Rated Performance (TLX)"), caption = paste("Participants who label their performance as", post_session_labled_performance) , y = y_lab_indep) +
  facet_grid(SessionOrder ~ Target)

post_session_labled_performance<- "Very poor"
plot_data_ind <- ind_data %>%
  select(Performance,
         params$dependent_response_ind,
         My_Performance,
         SessionOrder, 
         Target) %>%
  mutate(performance_reverse = 100 - Performance)%>%
  filter(My_Performance == post_session_labled_performance)

ggplot(data = plot_data_ind, aes(x = performance_reverse, y = .data[[params$dependent_response_ind]])) +
  geom_point() +
  labs(title = paste(y_lab_indep, "vs Self-Rated Performance (TLX)"), caption = paste("Participants who label their performance as", post_session_labled_performance) , y = y_lab_indep) +
  facet_grid(SessionOrder ~ Target)
```

No obvious violation of monotonic relationship.

```{r}

for (ind_rating in c("Excellent", "Good", "Average", "Poor", "Very poor")) {
  for (my_target in c("Ind", "Team", "Ind_Team")) {
    for (my_session in c(2:4)) {
      plot_data_ind <- ind_data %>%
        select(Performance,
               params$dependent_response_ind,
               SessionOrder,
               Dominate.Strategy,
               My_Performance,
               Target,
               Player_ID) %>%
        mutate(performance_reverse = 100 - Performance)%>% 
        filter(Target == my_target, My_Performance == ind_rating, SessionOrder == my_session)
      
      if(length(plot_data_ind[[params$dependent_response_ind]]) < 3){
        message<- paste("There is less than 3 data point for the Condition =", my_target, ", Session =", my_session, ", Rated individual Performance =", ind_rating)
        print(message)
      } else {
        cor_test_results<- cor.test(x = plot_data_ind[["performance_reverse"]], y = plot_data_ind[[params$dependent_response_ind]], method = "spearman")
        
        if(cor_test_results$p.value < 0.1)
          print(paste("Correltation: Condition =", my_target, ", Session =", my_session, ", Rated individual Performance =", ind_rating))
          print(cor_test_results$p.value)
      }
    }
  }
}
```
Condition = Ind , Session = 3 , Rated individual Performance = Excellent, __significant__
Condition = Ind_Team , Session = 4 , Rated individual Performance = Excellent, __significant__
Condition = Ind_Team , Session = 2 , Rated individual Performance = Poor, __marginally significant__

```{r}
# dependent<- "timeRemaining_ind"
current_target<- "Ind"
current_my_performance<-  "Excellent"
current_Session<- 3

plot_data_ind <- ind_data %>%
  select(Performance,
         params$dependent_response_ind,
         SessionOrder,
         Dominate.Strategy,
         My_Performance,
         Target,
         Player_ID) %>%
  mutate(performance_reverse = 100 - Performance) %>% 
  filter(Target == current_target, My_Performance == current_my_performance, SessionOrder == current_Session)

N_paris<- length(plot_data_ind[[params$dependent_response_ind]])

print(paste("Correltation: Condition =", current_target, ", Session =", current_Session, ", Rated individual Performance =", current_my_performance))

print(paste("Observations:", N_paris))

cor.test(y = plot_data_ind[[params$dependent_response_ind]], x = plot_data_ind[["performance_reverse"]], method = "spearman")

#----

current_target<- "Ind_Team"
current_my_performance<-  "Excellent"
current_Session<- 4

plot_data_ind <- ind_data %>%
  select(Performance,
         params$dependent_response_ind,
         SessionOrder,
         Dominate.Strategy,
         My_Performance,
         Target,
         Player_ID) %>%
  mutate(performance_reverse = 100 - Performance) %>% 
  filter(Target == current_target, My_Performance == current_my_performance, SessionOrder == current_Session)

N_paris<- length(plot_data_ind[[params$dependent_response_ind]])

print(paste("Correltation: Condition =", current_target, ", Session =", current_Session, ", Rated individual Performance =", current_my_performance))

print(paste("Observations:", N_paris))

cor.test(y = plot_data_ind[[params$dependent_response_ind]], x = plot_data_ind[["performance_reverse"]], method = "spearman")


```

When grouping paired responses for correct collection rate and performance (reverse) by Target, session order, and self reported performance (e.g., poor vs. excellent), the results show a __significant__ negative correlation for participants in Individual conditio in session 3 and labeled their performance as excellent, indicating a correct self-perception of performance. The results show a __significant__ negative correlation for participants in Ind_Team condition in session 4 and labaled their performance as Excellent. 

## Summary 

"When grouping paired responses for correct collection rate and performance (reverse) by Target, the results show a __significant__ negative correltation for the Team condition. Indicating correct self perception of performance. Results also show a __marginally significant__ negative correlation in the Ind_Team condition. "


"When grouping paired responses for correct collection rate and performance (reverse) by session order, the results show a __significant__ negative correlation for session 4. Indicating a correct perception of performance. The results also showed a __marginally significant__ negative correlation in session 2."

"When grouping paired responses for correct collection rate and performance (reverse) by target and session order, the results showed a __significant__ negative correlation for participants in Team in session 2, and for pariticpants in Ind_Team in session 4, indicating a correct perception."

"When grouping paired responses for correct collection rate and performance (reverse) by self reported performance (e.g., poor vs. excellent), the results show a __significant__ negative correlation for participants that rated their performance as Excellent, indicating a correct perception of performance. The results also showed a __singnificant__ positive correlation for participants that rated their performance as Poor, indiciating an incorrect perception of performance."


"When grouping paired responses for correct collection rate and performance (reverse) by session order and self reported performance (e.g., poor vs. excellent), the results showed a __significant__ negative correlations for participants in session 2 that rated themsleves as Excellent, indicating a correct perception. The results showed a __significant__ positive correlation for participants in session 2 that rated themselves as Poor, indicating an incorrect perception of performance. "

"When grouping paired responses for correct collection rate and performance (reverse) by Target, session order, and self reported performance (e.g., poor vs. excellent), the results show a __significant__ negative correlation for participants in Individual conditio in session 3 and labeled their performance as excellent, indicating a correct self-perception of performance. The results show a __significant__ negative correlation for participants in Ind_Team condition in session 4 and labaled their performance as Excellent. "



